---
output:
  word_document: default
  html_document: default
---

#< ignore

```{r "setup", eval=FALSE}

# Load required Packages
library(RTutor)
library(yaml)

#Set Working Directory
setwd("D:/Universitaet Ulm Unterlagen/Bachelorarbeit/The-Impact-Of-Reviews-And-Ratings-On-Bookmarket")

# Set problem set's name
ps.name = "The Impacts of reviews and Ratings on Book Market"; sol.file = paste0(ps.name,"_sol.Rmd")

# character vector of all required packages in the problem set
libs = c("ggplot2") 

#rps.has.sol=TRUE
# Create Problem Set
create.ps(sol.file=sol.file, ps.name=ps.name,libs=libs,stop.when.finished=FALSE, addons="quiz")

# Show the problem set in the webbrowser
show.ps(ps.name,sample.solution=FALSE,auto.save.code = TRUE)
```

#>

# The Impacts of Professional Reviews and Crowd Ratings on the Book Market

Author: Leonard Pöhls 

Hello readers and welcome to my Bachelor Thesis about how professional reviews and crowd ratings impacting the book market. Do not wonder about the manner of this Thesis. The whole Program is based on the statistical programming language R and its package RTutor to generate interactive problem sets with exercises for its readers. My created Problem is based on the Paper **Digitization and Pre-Purchase Information: The Causal and Welfare Impacts of Reviews and Crowd Ratings"** by Imke Reimers and Joel Waldfogel, that has been published in 2021 in the American Economic Journal. It investigates two main aspects. First, how pre-purchase information in the form of crowd ratings from other individual purchaser and professional reviews from daily newspapers do affect sales ranks and revenues. Second, to compare the welfare effect with and without the presence of pre-purchase information. The base of those mentioned welfare effects got determined through the transformation from sales prices and sales ranks into quantity elasticities. The Paper can be opened [here](https://www.aeaweb.org/articles?id=10.1257/aer.20200153). 

In 1995, one year after Amazon opened their gates, about more than 61% of all book sales in the USA has been generated by physical bookstores and bookclubs, while just 10 percent have been made from other channels including Amazon (Curcic, 2023). 

For the following 28 years we experienced the growth of digitization and development of crowd rating infrastructure on online pages. 
Hence, users got capable to receive important non-professional pre-information from other users that potentially influences purchasing behavior and economic welfare effects. As a result, online retailers substituted the trade of physical books in wide parts. From an economic perspective, pre-purchase information likewise effects personal expectation of quality and therefore also the demand.  

Today, the distribution of market share in print books have been changed significantly, while Amazon have taken over the leadership as the biggest retailer of print books in all over the world. For instance, the Amazon share for US book market accounts more than 40% percent and around 50% for the Uk market share (McLoughlin, 2022).

To examine these effects, this problem set aims to reorganize and replicate part of the study from Reimers and Waldfogel by retyping and extending their investigations about the effects of professional reviews and crowd ratings on sales ranks and revenues. 

## Content

1. Motivation

 1.1 Book Market, Professional Reviews and Crowd Ratings
 
 1.2 Introduction to Welfare, Demand and Price Elasticity

2. Data and Descriptice Insights

 2.1 Introduction to the Data Set
 
 2.2 Professional Reviews and Crowd Ratings
 
 2.3 Recognition of Potential Effects through Descriptive Approaches
 
3. Empirical Strategies on Sales Ranks 

 3.1 Introduction and Implementation of Event Studies
 
 3.2 Robust Standard Errors, Fixed Effects and Logarithmized Estimates
 
 3.3 Estimation of the Effects on Sales Ranks
 
4. Translating Sales Ranks into Quantities and Price Elasticity
 
5. Conclusion

6. References

Appendix - tbd.

A1. tbd.

A2. tbd.

A3. tbd.

## An Instruction how to work with Problem sets

As already mentioned above, the manner of this problem set is to create an interactive environment for its readers. Thus, sometimes appear different Types of exercises with a so called chunk (window) below. Basically, there are three different type of exercises:   
* An empty code chunk without any Information. Consequently, you have to find the solution by yourself. 
* Code chunks with gaps like ___ to replace with the correct code. 
* Those where the whole code is already given. This Code is ready to run.  
If you need some advice by solving the exercise, just press `hint` to get some help. By pressing `run` the code gets executed. The `solution` button is a short-cut to deliver the correct code immediately. To verify the task, click on `check`. If your code was not correct, you would get a corresponding report. 

Next to code chunks, you can also work on some multiple choice quizzes to test your prior knowledge or to check your own text comprehension. Guessing the right answer can also lead to a higher understanding and a maintaining attention. 

Press `Go to next exercise...` to continue and to find further instructive competitions.

<br/>

## Exercise 1 -- Motivation

In this study, the book market was chosen to determine the impacts from crowd ratings and professional reviews. 

First of all, the following chapter intends to declare the meaning of "pre-purchase information", the book market situation and why especially this market is predestined for measuring review effects. To find an answer, we focus on newspaper magazines and their turnus of releasing new reviews for books and on the role of Amazon concerning crowd ratings and so called sales ranks. 

In the second part of this chapter, we illustrate potential welfare effects by having access to pre-purchase information with and without the restriction of fixed book prices. Additionally, we explain the transition from sales ranks and sales prices into quantity elasticities.  
After editing this chapter, you gained an insight of the initial situation on the book market and you received deeper knowledge about basic economic issues. Thus you will be well prepared to continue with chapter 2. 

### Structure

1.1 Book Market, Professional Reviews and Crowd Ratings

1.2 Introduction to Welfare, Demand and Price Elasticity









## Exercise 1 -- Computing with R

a) We often want to compute some summary statistic of a vector. For example:

```{r}
#< task
x = 10:20
# Computing the sum of x
sum(x)
#>
```

Now compute the mean of x.
```{r optional=TRUE}
# Note the chunk option optional = TRUE means
# the user can continue with the next exercise
# without having solved this one

mean(x)
#< hint
cat("There already exist R functions for many things. To find them use Google, e.g. search for 'R compute mean'.")
#>
```


#< info "useful functions for numeric vectors"
Here are examples for useful R functions
```{r}
max(c(1,5,2)) # returns maximum
min(c(1,5,2)) # returns minimum

sum(c(1,5,2,NA), na.rm=TRUE) # returns sum of all numbers, ignore NA
cumsum(c(1,5,2)) # returns cummulated sum
diff(c(1,5,2)) # returns the vector of differences
```
#>


#< award "mean means mean"
Well, in some occasions one can just guess the name of an R function. The function to compute the mean of a vector, or matrix is called 'mean'. Usually, it is much quicker to goggle than to guess function names, however.
#>

b) Let `y` be a vector that contains the squared elements of `x`, i.e. for each element $i$ we want $$y_i = x_i^2.$$ Then show `y`.
```{r}
# We should not set this chunk optional
# since we need y in the next chunk
y = x^2
y
```

#c) Now use the function `qplot` from the package `ggplot2` to create a scatter plot of `x` against `y`. You can google `r qplot` to get the help for #the function `qplot`.

```{r optional=TRUE, dev="svg", fig.width=4}
#< task
library(ggplot2) # load ggplot2 package

# Enter your call to qplot here...
#>
qplot(x,y)
#< test_arg
allow.extra.arg = TRUE 
#>
# The block above allows the user to add extra arguments to the call to qplot, i.e. qplot(x,y,xlab="The variable x"), would also pass the test.
```


#< quiz "prime"
question: What is the 'oddest' prime?
sc:
    - 2*
    - 3
    - 5
    - 7
success: Well, of course the answer is debatable...
failure: Try again.
#>

Note: A quiz as specified below only works in the shiny environment. If you want to design a quiz in an RMarkdown based RTutor problem set, you should use a chunk. E.g. as follows:

Which of the following numbers is the oddest prime? 2,3,5 or 7? Enter you solution in the code below and press "check".

```{r}
2
```
#< award "The oddest prime"
Wouldn't you agree that the only even prime is the odd man out?
#>

## Exercise Submitting your solution

To submit your solution please proceed as follows:

1. Scroll to the top and click on the icon with the bars <i class="fa fa-tasks fa-fw"></i> to see how many points you got so far. If you want to have more points you can try to solve the missing tasks.

2. If you want to submit click on the download button <i class="fa  fa-download fa-fw"></i> at the very right.

3. In the opened tab click the button "Download Submission File". Your browser should then download a file with the extension `.sub`.

4. Upload that downloaded file to your course management system like Moodle, as specified by your instructor.



