
---
title: Problem Set The Impacts of reviews and Ratings on Book Market
output: 
  html_document: 
    keep_md: yes
    toc: yes
---

```{r setup, include=FALSE, echo=FALSE}
# Load libraries and source extra code
library(ggplot2)
library(tidyverse)
library(RTutor)


# Options for rendering data frames
# If you knit to a Word docx file, try
# 
# data.frame.theme="word" 
# 
# (needs RStudio > 1.2.1)
# 
# You can also set the options like
# table.max.cols as chunk options
# Makes sense if there are too many, too wide
# columns in some chunks

RTutor::set.knit.print.opts(data.frame.theme="code", table.max.rows=25, table.max.cols=NULL, round.digits=5, signif.digits=8)


# continue knitting even if there is an error
knitr::opts_chunk$set(error = TRUE) 
```



# The Impacts of Professional Reviews and Crowd Ratings on the Book Market

Author: Leonard Pöhls 

Hello readers and welcome to my Bachelor Thesis about how professional reviews and crowd ratings impacting the book market. Do not wonder about the manner of this Thesis. The whole Program is based on the statistical programming language R and its package RTutor to generate interactive problem sets with exercises for its readers. My created Problem is based on the Paper **Digitization and Pre-Purchase Information: The Causal and Welfare Impacts of Reviews and Crowd Ratings"** by Imke Reimers and Joel Waldfogel, that has been published in 2021 in the American Economic Journal. It investigates two main aspects. First, how pre-purchase information in the form of crowd ratings from other individual purchaser and professional reviews from daily newspapers do affect sales ranks and revenues. Second, to compare the welfare effect with and without the presence of pre-purchase information. The base of those mentioned welfare effects got determined through the transformation from sales prices and sales ranks into quantity elasticities. The Paper can be opened [here](https://www.aeaweb.org/articles?id=10.1257/aer.20200153). 

In 1995, one year after Amazon opened their gates, about more than 61% of all book sales in the USA has been generated by physical bookstores and bookclubs, while just 10 percent have been made from other channels including Amazon (Curcic, 2023). 

For the following 28 years we experienced the growth of digitization and development of crowd rating infrastructure on online pages. 
Hence, users got capable to receive important non-professional pre-information from other users that potentially influences purchasing behavior and economic welfare effects. As a result, online retailers substituted the trade of physical books in wide parts. From an economic perspective, pre-purchase information likewise effects personal expectation of quality and therefore also the demand.  

Today, the distribution of market share in print books have been changed significantly, while Amazon have taken over the leadership as the biggest retailer of print books in all over the world. For instance, the Amazon share for US book market accounts more than 40% percent and around 50% for the Uk market share (McLoughlin, 2022).

To examine these effects, this problem set aims to reorganize and replicate part of the study from Reimers and Waldfogel by retyping and extending their investigations about the effects of professional reviews and crowd ratings on sales ranks and revenues. 

## Exercise Content

1. Motivation

 1.1 Book Market, Professional Reviews and Crowd Ratings
 
 1.2 Introduction to Welfare, Demand and Price Elasticity

2. Data and Descriptice Insights

 2.1 Introduction to the Data Set
 
 2.2 Professional Reviews and Crowd Ratings
 
 2.3 Recognition of Potential Effects through Descriptive Approaches
 
3. Empirical Strategies on Sales Ranks 

 3.1 Introduction and Implementation of Event Studies
 
 3.2 Robust Standard Errors, Fixed Effects and Logarithmized Estimates
 
 3.3 Estimation of the Effects on Sales Ranks
 
4. Translating Sales Ranks into Quantities and Price Elasticity
 
5. Conclusion

6. References

Appendix - tbd.

A1. tbd.

A2. tbd.

A3. tbd.

## An Instruction how to work with Problem sets

As already mentioned above, the manner of this problem set is to create an interactive environment for its readers. Thus, sometimes appear different Types of exercises with a so called chunk (window) below. Basically, there are three different type of exercises:   
* An empty code chunk without any Information. Consequently, you have to find the solution by yourself. 
* Code chunks with gaps like ___ to replace with the correct code. 
* Those where the whole code is already given. This Code is ready to run.  
If you need some advice by solving the exercise, just press `hint` to get some help. By pressing `run` the code gets executed. The `solution` button is a short-cut to deliver the correct code immediately. To verify the task, click on `check`. If your code was not correct, you would get a corresponding report. 

Next to code chunks, you can also work on some multiple choice quizzes to test your prior knowledge or to check your own text comprehension. Guessing the right answer can also lead to a higher understanding and a maintaining attention. 

Press `Go to next exercise...` to continue and to find further instructive competitions.

<br/>


## Exercise 1 -- Motivation

In this study, the book market was chosen to determine the impacts from crowd ratings and professional reviews. 

First of all, the following chapter intends to declare the meaning of "pre-purchase information", the book market situation and why especially this market is predestined for measuring review effects. To find an answer, we focus on newspaper magazines and on the role of Amazon concerning crowd ratings and so called sales ranks. 

In the second part of this chapter, we illustrate potential welfare effects by having access to pre-purchase information with and without the restriction of fixed book prices. Additionally, we explain the transition from sales ranks and sales prices into quantity elasticities.  
After editing this chapter, you gained an insight of the initial situation on the book market and you received deeper knowledge about basic economic issues. Thus you will be well prepared to continue with chapter 2. 

### Structure

1.1 Book Market, Professional Reviews and Crowd Ratings

1.2 Introduction to Welfare, Demand and Price Elasticity


## Exercise 1.1 -- Book Market, Professional Reviews and Crowd Ratings

Generally, economists differentiate goods concerning their characteristics, their occurrences or other conditions. Focusing the degree of uncertainty, we distinguish between three different goods, **Search Goods**, **Experience Goods** and **Credence Goods**. Buyer of **Search Goods** already have an accurate perception and a high degree of certainty of what they want to buy. For instance, sugar or computer are typical search goods. **Experience Goods** are associated with a lower degree of certainty. Without any information advantages, buyers are not capable to assess the goods quality until the buyer starts comsuming it, such as visits to cinema or whine. By the consumption of **Credence Goods** the buyer never gets into the situation to evaluate the quality of the underlying good as the degree of uncertainty is the highest here. Common credence goods are services like lawyers or surgeons (Wieneke, 2019). 


Quiz: What would you guess books belong to?

- Search Goods. [ ]

- Experience Goods. [x]

- Credence Goods. [ ]


The underlying paper focuses the book market to examine the impacts from crowd ratings and professional reviews on sales ranks. So why is particulary the book market that appropriated for this study? In the underlying paper, Reimers and Waldfogel enumerated three main reasons for this claim. First, books belong to experience goods. For the other two goods, pre-purchase information is less or not relevant. Second, the number of professional reviews (in high visible media) is relatively small and distributed across a few big newspapers. The third reason refers to the data set on which the entire examination is based on. The high frequently data on book demand at Amazon should contain about 45% of the US physical book market, what is approximately comparable to Mcloughlins numbers from 2022. 

As explained, professional reviews are defined as periodically appearing reviews in daily newspaper articles. The data set includes information about the appearance of professional reviews from the New York Times, the Chicago Tribune, the Boston Globe, the Wall Street Journal, the Los Angeles Times and the Washington Post. However, quantitative information as well as star ratings are not available. Additionally, The New York Times recommends nine books every week (New York Times, 2023). Professional reviews enable access to pre-purchase information. 


Quiz: What is your suggestion, which of these newspapers has the most impact on the sales quantity?

- The New York Times. [x]

- The Chicago Tribune. [ ]

- The Boston Globe. [ ]

- The Wall Street Journal. [ ]

- The Los Angeles Times. [ ]

- The Washington Post. [ ]


As well as professional reviews, the Amazon data set also includes information about star ratings from buyers. Identified as buyer on Amazon, everyone is permitted to evaluate the bought product on a five-point scale. Basically, people benefit from other customers reviews. However, in contrast to professional reviews, crowd rating are tending to generate less trust. Crowd ratings are susceptible to fake content for defaming or fraudulent purposes while professional reviews were created by objective and professional reviewers. Therefore, the more ratings exist for the particular product, the more likely the calculated average star rating approximates the "actual" quality. Thus crowd ratings are representing the second pre-purchase information.                                                                 
 
Hence, Reimers and Waldfogel claim that the consumer interacts with both of these types of pre-purchase information in a different way, perhaps resulting in different or superimposed effects. One possible reason could be the difference in accessibility of these information types. While crowd ratings are visible for every Amazon user, professional reviews are accessible but not automatically visible for everyone. Furthermore, it is less likely that people who randomly find a book on Amazon will verify the existence of a professional review afterwards. Vice versa, after finding a professional reviewed book, people automatically get access to crowd ratings during the purchasing process. Incidentally, word-of-mouth can be also understood as pre-purchase information. Nevertheless, the consumer has access to at least one type of pre-purchase information. 



Quiz: How many reviews on Amazon are fake or unreliable?

- 61%. [ ]

- 23%. [ ]

- 9%. [ ]

- 42%. [x]

- 15%. [ ]



Previously, we mentioned to aim an estimation on so called sales ranks. Sales ranks are the numerical representation of how your products sells in contrast to other products in the same categorie (Wisniach, 2022). Actually, we do not have information about sold quantities so that sales ranks are substituting these values. [Amazon](https://www.amazon.com/gp/help/customer/display.html?nodeId=GGGMZK378RQPATDJ) defined their sales rank as hourly updated calculation to "reflect recent recent and historical sales of every item sold on Amazon". Hence, sales ranks are relative numbers to compare sales activities. To make assumptions regarding to a welfare analysis, the authors of the underlying paper collected more data from New York Times top-100 weekly bestsellers from 2018 to transform ranks into quantities. As a result, we are capable to examine price elasticities. 

**Summary**

To sum up, we obtained an explanation of goods concerning their level of certainty and assigned books to the experience goods. Furthermore, we enumerated three different types of pre-purchase information from which we use two for the estimation. We recognized that crowd ratings and professional reviews exhibit different effects and potentially superimpose each other what possibly leads to different results in estimation. Finally, we got an introduction to Amazons sales ranks and their importance for the further course. 

In the following chapter 1.2, you will pick up the economic basic knowledge you need to understand the analysis and the manner of this examination. 

## Exercise 1.2 -- Introduction to Welfare, Demand and Price Elasticity

Colloquially, the term "welfare" is associated with many contexts, such as unemployment benefit or other social assistance. The actual origin of this term lies in the economy. Mathematically, welfare is sum of producer surplus and consumer surplus. Basically, consumer surplus is the difference between the price for a good that consumers are willing to pay and the actual price of this good. Against this, Producer surplus is the difference between the price that suppliers would be willing to charge for their goods and the actual price of this good. Actually, the economic reality is much more complex. For simplifying purposes, we focus on polypol markets (markets with many suppliers) under perfect conditions, that the model requires in order to work. Without even one of these assumptions, the model is invalid.   


Quiz: Which of these conditions is **not** relevant for a perfect market?

- Perfect information availability (Knowledge about every price for the underlying good). [ ]

- No personal preferences (Preferences, that prevent you from acting rationally). [ ]

- Homogenous goods (Equal goods). [ ]

- Fast reaction velocity (Changing market conditions are quickly recognized from every market participant). [ ]

- Every good has the same quality. [x]

- A large number of demanders and suppliers. [ ]


Under these conditions, we apply a graph to illustrate the situation between demand and supply to better understand the added value of pre-purchase information. 

**Task:** Run the following chunk to create this model. Press `check` to collect your points. 

```{r "4_1"}
#Create a fictive Dataset 
demand <- c(2, 1.5, 1, 0.5, 0)
xAxis <- c(0, 1,2,3,4)
supply <- c(0, 0.5, 1, 1.5, 2)
xGroup <- c(1, 1, 1, 1, 1)
DatasetTest <- data.frame(Price = demand, Quantity = xAxis, Supply = supply, Group = xGroup)
#Create a plot
ggplot(data = DatasetTest) +
  geom_line(aes(x=Quantity, y=Price, group = Group), linetype = 1, size = 0.8) +
  geom_line(aes(x=Quantity, y=supply, group = Group), linetype = 1, size = 0.8) +
  geom_segment(aes(x = 2, y = 0, xend = 2, yend = 1), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 0, y = 1, xend = 2, yend = 1), color = "red", linetype = "dashed") +
#Mark Zone A
  geom_text(aes(x=0.5, y=1.3, label = "A"), color = "black", hjust=0, size=8, alpha = 0.1) +
#Mark Zone B
  geom_text(aes(x=0.5, y=0.7, label = "B"), color = "black", hjust=0, size=8, alpha = 0.1) +
#Mark Zone C
  geom_text(aes(x=1.5, y=0.3, label = "C"), color = "black", hjust=0, size=8, alpha = 0.1) +  
#Mark intersection point
  geom_point(aes(x = 2, y=1), color = "red", size=2.5) +
#Add line description
geom_text(aes(x=0.5, y=1.83, label = "Demand"), color = "Black", angle = 315, size= 4, alpha=0.1) +
geom_text(aes(x=3.35, y=1.78, label = "Supply"), color = "Black", angle = 45, size= 4, alpha=0.1) +
#Set specific layout
  theme_bw() +
  labs(title = "How is Pre-Purchase Information related to Welfare?",
       x = "Quantity", 
       y = "Price") +
  scale_x_continuous(labels = c("0", "", "Q*", "", "")) +
  scale_y_continuous(labels = c("0", "", "P*", "", "")) +
  theme(
 # axis.text.y=element_blank(),
  panel.grid.minor=element_blank(),plot.background=element_blank())


```

The linear demand curve shows how the consumers act on a perfect market. Obviously, a maximum price exists at which no more is consumed. This model likewise assumes unrealistically that free goods are consumed infinitely. On the other side, the linear supply curve illustrates the suppliers point of view. The model concludes that every supplier can offer his good for the maximum price. Vice versa, the more the price falls, the fewer suppliers can still offer their good.     In natural competition, suppliers are forced to align their prices. This is due to the fact that each supplier wants to maximize its revenue, so it is not worthwhile for the suppliers who can offer the lowest price to actually offer the lowest price. In long term, the actual market price will converge to P* and every supplier that can not offer for P* disappears. Finally, P* defines the equilibrium price and Q* the equilibrium quantity.  


Quiz: Which of these marked triangles represents the consumer surplus?

- A. [x]

- B. [ ]

- C. [ ]


**Price Elasticity**

As already mentioned, the previous model was a severe simplification of a complex market. For instance, the fiscus also impacts market activity by implementing price caps, by subsidizing various branches or in ensuring that no so called price cartels are created. Price cartels are an association of organizations closing price agreements for particular goods to bypass the competition. Usually, the course of the two curves is not linear and the conditions for a perfect market are not satisfied. The slope of the demand or supply curve depends on the so called **Price Elasticity**. For the demand side, **Price elasticity** indicates how demand reacts on changes in prices relatively. The formula looks as follows:  

$$
 \epsilon = \frac{\Delta Q/Q}{\Delta P/P} =  \frac{\%\,\mathrm{Change\,in\,the\,quantity\,of\,goods\,demanded}}{\%\,\mathrm{Change\,in\,price}}
$$

Hence, price elasticity delivers a value ε := [0, ∞] that can also show whether price increases would be worthwhile. An elasticity of ε = 1 tells us that a price increase of one percents implies a demand decrease of one percent and represents the maximum turnover point for suppliers. As a result, elasticities of ε < 1 are inelastic and otherwise elastic.   


Quiz: You are bar owner and want to maximize your turnover. In a particular period of time, you found out that the demand on beer is linear and a price increase from 3 Units to 4 Units implies a decreasing sales quantity from 1000 quantity units to 875 quantity units. Which of the following responses is correct?

- The price is inelastic - You should not increase the price. [ ]

- The price is elastic - You should increase the price by 47%. [ ]

- The price is inelastic - You should increase the price by 34%. [ ]

- The price is inelastic - You can easily more than double the price. [x]


Price elasticity can be also shown graphically. The following graph illustrates the difference between elasticities in demand. 

**Task:** Execute the chunk below to see how the demand curve slope changes with different price elasticities

```{r "4_2"}
#Create a fictive Dataset 
DatasetPE <- data.frame(
  Price = 1:10,
  Demand_05 = 10 - 0.5*1:10,
  Demand_1 = 10 - 1*1:10,
  Demand_2 = 10 - 2*1:10
)
colnames(DatasetPE) <- c("Price", "ε > 1", "ε = 1", "ε < 1")

DatasetPE <- DatasetPE %>% 
  pivot_longer(cols = starts_with("ε"), names_to = "ε", values_to = "Quantity_Value") 

# Umwandeln der Daten in "long format"
ggplot(data = DatasetPE, aes(x = Price, y = Quantity_Value, group = ε)) +
  geom_line() +
  theme_bw() +
  geom_segment(aes(x = 4, y = 8, xend = 4, yend = 9), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 4, y = 9, xend = 2, yend = 9), color = "red", linetype = "dashed") +
  geom_text(aes(x=2.75, y=9.25, label = "ΔQU = 2"), color = "red", hjust=0, size=2.5, alpha = 0.1) +
  geom_text(aes(x=4.25, y=8.95, label = "ΔPU = 1"), color = "red", angle = 270, hjust=0, size=2.5, alpha = 0.1) +
  geom_text(aes(x=5, y=7.85, label = "ε > 1"), color = "black", angle = 337.5, hjust=0, size=5, alpha = 0.1) +
  
  geom_segment(aes(x = 4, y = 6, xend = 4, yend = 7), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 4, y = 7, xend = 3, yend = 7), color = "red", linetype = "dashed") +
  geom_text(aes(x=3.15, y=7.2, label = "ΔQU = 1"), color = "red", hjust=0, size=2.5, alpha = 0.1) +
  geom_text(aes(x=4.25, y=6.9, label = "PU = 1"), color = "red", angle = 270, hjust=0, size=2.5, alpha = 0.1) +
  geom_text(aes(x=5, y=5.45, label = "ε = 1"), color = "black", angle = 315, hjust=0, size=5, alpha = 0.1) +
  
  geom_segment(aes(x = 4, y = 2, xend = 4, yend = 4), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 4, y = 4, xend = 3, yend = 4), color = "red", linetype = "dashed") +
  geom_text(aes(x=3.15, y=4.2, label = "ΔQU = 1"), color = "red", hjust=0, size=2.5, alpha = 0.1) +
  geom_text(aes(x=4.25, y=3.45, label = "ΔPU = 2"), color = "red", angle = 270, hjust=0, size=2.5, alpha = 0.1) +
  geom_text(aes(x=4.6, y=1.7, label = "ε < 1"), color = "black", angle = 292.5, hjust=0, size=5, alpha = 0.1) +
  
  labs(title = "Demand Curves and their Price Elasticities",
       x = "Quantity in QU (Quantity Units)", 
       y = "Price in PU (Price Units)") +
  xlim(0, 10) + 
  ylim(0, 10) +
  scale_x_continuous(breaks = 0:10) +
  theme(panel.grid.minor=element_blank(),plot.background=element_blank()) 
```

Returning to the subject of pre-purchase information, a clear classification of these are needed. Alan T. Sorensen and Kenneth Train claimed that pre-purchase information changes the perception of the books quality and that a distinction between anticipated ex ante utility and experienced ex post utility is needed to measure the effect of these information on welfare. In simpler terms, we assume that a consumer obtains a different use depending on the availability of pre-purchase information. In sum, the consumer could face three various situations depending on the books expected quality. The consumer can expect lower quality than the actual quality $$(\bar R_{j} < R_{j})$$, the same quality $$(\bar R_{j} = R_{j})$$ or a higher expected quality than the actual quality $$(\bar R_{j} > R_{j})$$. 

```{r "4_3"}
#Create a fictive Dataset 
yPredQualityPrice <- c(1.6,1.0,0.50,0.15,-0.10)
xQuan <- c(1,2,3,4,5)
yRealQualityPrice <- c(2.1,1.5,1,0.65,0.4)
xGroup <- c(1, 1, 1, 1, 1)
DatasetTest <- data.frame(Pred_Price = yPredQualityPrice, Quan = xQuan, Real_Price = yRealQualityPrice, Group = xGroup)

#Create a plot
ggplot(data = DatasetTest) +
  geom_line(aes(x=Quan, y=Pred_Price, group = Group), linetype = 2, size = 0.9) +
  geom_line(aes(x=Quan, y=Real_Price, group = Group), linetype = 1, size = 0.9) +
  geom_segment(aes(x = 2, y = 0, xend = 2, yend = 1), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 3, y = 0, xend = 3, yend = 1), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 4, y = 0, xend = 4, yend = 1), color = "red", linetype = "dashed") +
  geom_segment(aes(x = 0, y = 1, xend = 5, yend = 1),size=1.1, color = "red") +

#Mark Zone A
  geom_text(aes(x=1.25, y=1.15, label = "A"), color = "black", hjust=0, size=5, alpha = 0.1) +
  geom_segment(aes(x = 1, y = 1, xend = 1, yend = 1.5), color = "black", linetype = "dashed") +
#Mark Zone B
  geom_text(aes(x=1.5, y=1.5, label = "B"), color = "black", hjust=0, size=5, alpha = 0.1) +
  geom_segment(aes(x = 1, y = 1.5, xend = 1, yend = 2.1), color = "black", linetype = "dashed") +
  geom_segment(aes(x = 2, y = 1, xend = 2, yend = 1.5), color = "black", linetype = "dashed") +
#Mark Zone C
  geom_text(aes(x=2.27, y=1.17, label = "C"), color = "black", hjust=0, size=5, alpha = 0.1) +
#Mark Zone D
  geom_text(aes(x=3.6, y=0.9, label = "D"), color = "black", hjust=0, size=5, alpha = 0.1) +
  geom_segment(aes(x = 4, y = 0.65, xend = 4, yend = 1), color = "black", linetype = "dashed") +
#Mark intersection points
  geom_point(aes(x = 2, y=1), color = "red", size=2.5) +
  geom_point(aes(x = 4, y=1), color = "red", size=2.5) +
  geom_text(aes(x=1.8, y=0.93, label = "P1"), color = "black", hjust=0, size=3, alpha = 0.1) +
  geom_text(aes(x=3.8, y=0.93, label = "P2"), color = "black", hjust=0, size=3, alpha = 0.1) +

#Add line description
  geom_text(aes(x=0, y=1.55, label = "Without \nPre-Purchase Information\n _ _ _ _ _ _ _ _ _ _ _ _ "), color = "Black", hjust=0, size= 2.2, alpha=0.1) + 
  geom_text(aes(x=0, y=2.05, label = "With \nPre-Purchase Information\n ___________________"), color = "Black", hjust=0, size= 2.2, alpha=0.1) +
  
#Set specific layout
  theme_bw() +
  labs(title = "How is Pre-Purchase Information related to Welfare?",
       x = "Quantity", 
       y = "Price") +
  scale_x_continuous(breaks = 1:5, labels = c("", "Q1", "Q*", "Q2", "")) +
  theme(
  axis.text.y=element_blank(),
  panel.grid.minor=element_blank(),plot.background=element_blank())
```

As visualized in the upper graph, the consumer would choose quantity Q1 for $$(\bar R_{j} < R_{j})$$






Now compute the mean of x.
```{r "4_4",optional=TRUE}
# Note the chunk option optional = TRUE means
# the user can continue with the next exercise
# without having solved this one
#
#\epsilon = \frac{\%\,\mathrm{Change\,in\,the\,quantity\,of\,goods\,demanded}}{\%\,\mathrm{Change\,in\,price}}
mean(x)
```



***

### Info: useful functions for numeric vectors
Here are examples for useful R functions
```{r "4_5"}
max(c(1,5,2)) # returns maximum
min(c(1,5,2)) # returns minimum

sum(c(1,5,2,NA), na.rm=TRUE) # returns sum of all numbers, ignore NA
cumsum(c(1,5,2)) # returns cummulated sum
diff(c(1,5,2)) # returns the vector of differences
```

***




***

### Award: mean means mean
Well, in some occasions one can just guess the name of an R function. The function to compute the mean of a vector, or matrix is called 'mean'. Usually, it is much quicker to goggle than to guess function names, however.

***


b) Let `y` be a vector that contains the squared elements of `x`, i.e. for each element $i$ we want $$y_i = x_i^2.$$ Then show `y`.
```{r "4_b_6"}
# We should not set this chunk optional
# since we need y in the next chunk
y = x^2
y
```

#c) Now use the function `qplot` from the package `ggplot2` to create a scatter plot of `x` against `y`. You can google `r qplot` to get the help for #the function `qplot`.

```{r "4_b_7",optional=TRUE, dev='svg', fig.width=4}
library(ggplot2) # load ggplot2 package

# Enter your call to qplot here...
qplot(x,y)
# The block above allows the user to add extra arguments to the call to qplot, i.e. qplot(x,y,xlab="The variable x"), would also pass the test.
```



Quiz: What is the 'oddest' prime?

- 2 [x]

- 3 [ ]

- 5 [ ]

- 7 [ ]


Note: A quiz as specified below only works in the shiny environment. If you want to design a quiz in an RMarkdown based RTutor problem set, you should use a chunk. E.g. as follows:

Which of the following numbers is the oddest prime? 2,3,5 or 7? Enter you solution in the code below and press "check".

```{r "4_b_8"}
2
```

***

### Award: The oddest prime
Wouldn't you agree that the only even prime is the odd man out?

***


## Exercise Submitting your solution

To submit your solution please proceed as follows:

1. Scroll to the top and click on the icon with the bars <i class="fa fa-tasks fa-fw"></i> to see how many points you got so far. If you want to have more points you can try to solve the missing tasks.

2. If you want to submit click on the download button <i class="fa  fa-download fa-fw"></i> at the very right.

3. In the opened tab click the button "Download Submission File". Your browser should then download a file with the extension `.sub`.

4. Upload that downloaded file to your course management system like Moodle, as specified by your instructor.



